COG-ED Manuscript

### 2021-08-19 06_Paper/COG-ED/Manuscript.Rmd
AUC calculation does not work yet

  library(here)         # to set a directory without defined paths
  library(tidyverse)    # plotting and managing data

@@

>>>>

  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package

@@

#auc(data_SV$level[1:4], data_SV$sv[1:4], method = "trapezoid", sort = FALSE) ->> gives you 2.23, which can't be
